RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-10-11 doc/paper.tex
Images for random instances.

\setcounter{tocdepth}{3}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{comment}
\usepackage{placeins}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
 \usepackage{booktabs}
\usepackage{array}
\usepackage[pdfencoding=auto,psdextra]{hyperref}
\usepackage{booktabs}
\usepackage{bookmark}% faster updated bookmarks
\usepackage{hypcap} % fix the links
\evensidemargin\oddsidemargin
\usepackage{graphicx}
\pagestyle{plain}
\usepackage{xcolor}
\newcommand\ToDo[1]{\textcolor{red}{#1}}
 \usepackage{tabularx}
\usepackage{xspace}
\usepackage{color}
\usepackage{epsfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
%\usepackage{changes}
\usepackage{tikz}
\usepackage{fullpage}
\usepackage{calc}
\usetikzlibrary{positioning,shadows,arrows,trees,shapes,fit}
\usepackage{blindtext}

@@

>>>>

\setcounter{tocdepth}{3}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{comment}
\usepackage{placeins}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
 \usepackage{booktabs}
\usepackage{array}
\usepackage[pdfencoding=auto,psdextra]{hyperref}
\usepackage{booktabs}
\usepackage{bookmark}% faster updated bookmarks
\usepackage{hypcap} % fix the links
\evensidemargin\oddsidemargin
\usepackage{graphicx}
\pagestyle{plain}
\usepackage{xcolor}
\newcommand\ToDo[1]{\textcolor{red}{#1}}
 \usepackage{tabularx}
\usepackage{xspace}
\usepackage{color}
\usepackage{epsfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
%\usepackage{changes}
\usepackage{tikz}
\usepackage{fullpage}
\usepackage{calc}
\usetikzlibrary{positioning,shadows,arrows,trees,shapes,fit}
\usepackage{blindtext}
\usepackage{pgfplots}
\pgfplotsset{compat=1.16}

@@

\begin{center}
 \begin{tikzpicture}
 	\begin{axis}[
		xlabel=$size$,
		ylabel=$exact\;percentage$,
		xmin=0, xmax=4,
		ymin=0, ymax=100,
		xtick={1,2,3},
		xticklabels={small,medium,large},   % <---
		ytick={0,10,...,100}
		]
		\addplot[smooth,mark=*,blue] plot coordinates {
			(1,85)
			(2,42.5)
			(3,21.05)
		};
		\addlegendentry{No noise}

		\addplot[smooth,color=red,mark=x]
		plot coordinates {
			(1,51.67)
			(2,13.75)
			(3,5.26)
		};
		\addlegendentry{Noise level 0.001}

		\addplot[smooth,color=green,mark=o]
		plot coordinates {
			(1,31.67)
			(2,5)
			(3,4.21)
		};
		\addlegendentry{Noise level 0.01}
	\end{axis}
\end{tikzpicture}
\captionof{figure}{Exact solution percentages for varying levels of noise and formulae sizes}
\label{fig:compExact_noise_size}
\end{center}

\begin{center}
	\begin{tikzpicture}
		\begin{axis}[
			xlabel=$size$,
			ylabel=$R^2 > 0.999\;percentage$,
			xmin=0, xmax=4,
			ymin=20, ymax=100,
			xtick={1,2,3},
			xticklabels={small,medium,large},   % <---
			ytick={20,30,...,100}
			]
			\addplot[smooth,mark=*,blue] plot coordinates {
				(1,98.33)
				(2,62.5)
				(3,58.95)
			};
			\addlegendentry{No noise}

			\addplot[smooth,color=red,mark=x]
			plot coordinates {
				(1,93.33)
				(2,53.75)
				(3,40)
			};
			\addlegendentry{Noise level 0.001}

			\addplot[smooth,color=green,mark=o]
			plot coordinates {
				(1,65)
				(2,31.25)
				(3,20)
			};
			\addlegendentry{Noise level 0.01}
		\end{axis}
	\end{tikzpicture}
	\captionof{figure}{Percentages of solutions having $R^2 > 0.999$ for varying levels of noise and formulae sizes}
	\label{fig:compR2_noise_size}
\end{center}

\begin{center}
	\begin{tikzpicture}
		\begin{axis}[
			xlabel=$variable\;count$,
			ylabel=$exact\;percentage$,
			xmin=0, xmax=6,
			ymin=0, ymax=100,
			xtick={1,2,3,4,5},
			xticklabels={1,2,3,4,5},   % <---
			ytick={0,10,...,100}
			]
			\addplot[smooth,mark=*,blue] plot coordinates {
				(1,52.31)
				(2,50)
				(3,44)
				(4,37.78)
				(5,13.33)
			};
			\addlegendentry{No noise}

			\addplot[smooth,color=red,mark=x]
			plot coordinates {
				(1,16.92)
				(2,21.67)
				(3,28)
				(4,17.78)
				(5,6.67)
			};
			\addlegendentry{Noise level 0.001}

			\addplot[smooth,color=green,mark=o]
			plot coordinates {
				(1,9.23)
				(2,15)
				(3,12)
				(4,11.11)
				(5,6.67)
			};
			\addlegendentry{Noise level 0.01}
		\end{axis}
	\end{tikzpicture}
	\captionof{figure}{Exact solution percentages for varying levels of noise and variable counts}
	\label{fig:compExact_noise_varcnt}
\end{center}

\begin{center}
	\begin{tikzpicture}
		\begin{axis}[
			xlabel=$variable\;count$,
			ylabel=$exact\;percentage$,
			xmin=0, xmax=6,
			ymin=0, ymax=100,
			xtick={1,2,3,4,5},
			xticklabels={1,2,3,4,5},   % <---
			ytick={0,10,...,100}
			]
			\addplot[smooth,mark=*,blue] plot coordinates {
				(1,86.15)
				(2,75)
				(3,72)
				(4,48.89)
				(5,40)
			};
			\addlegendentry{No noise}

			\addplot[smooth,color=red,mark=x]
			plot coordinates {
				(1,64.62)
				(2,66.67)
				(3,62)
				(4,40)
				(5,40)
			};
			\addlegendentry{Noise level 0.001}

			\addplot[smooth,color=green,mark=o]
			plot coordinates {
				(1,32.31)
				(2,43.33)
				(3,46)
				(4,24.44)
				(5,13.33)
			};
			\addlegendentry{Noise level 0.01}
		\end{axis}
	\end{tikzpicture}
	\captionof{figure}{Percentages of solutions having $R^2 > 0.999$ for varying levels of noise and variable counts}
	\label{fig:compR2_noise_varcnt}
\end{center}
